Network Configuration Synthesis with Abstract Topologies \vspace{1cm}

### 2017-03-12 paper/abstraction/paper.tex
more edits to section 7. Remove paragraph widows

\authorinfo{Ryan Beckett}{Princeton}{}
\authorinfo{Ratul Mahajan}{Microsoft}{}
\authorinfo{Todd Millstein}{UCLA}{}
\authorinfo{Jitendra Padhye}{Microsoft}{} 
\authorinfo{David Walker}{Princeton}{}

%\author{%
%Ryan Beckett\\
%  \affaddr{Princeton}
%  %\\
%  %\email{rbeckett@princeton.edu}
%\and
%Ratul Mahajan\\
%  \affaddr{Microsoft}
%  %\\
%  %\email{ratul@microsoft.com}
%\and
%Todd Millstein\\
%  \affaddr{UCLA}
%  %\affaddr{University of California, Los Angeles}
%  %\\
%  %\email{todd@cs.ucla.edu}
%\and
%Jitendra Padhye\\
%  \affaddr{Microsoft}
%  %\\
%  %\email{padhye@microsoft.com}
%\and
%David Walker\\
%  \affaddr{Princeton}
%  %\\
%  %\email{dpw@princeton.edu}
%}

@@

\textbf{Abstract---}
We develop \sysname, a system to synthesize provably-correct
BGP configurations for large, evolving networks from high-level
specifications of topology, routing policy, and fault-tolerance
requirements. \sysname is based on new abstractions for capturing
parameterized network topologies and their evolution, and algorithms
to analyze the impact of topology and routing policy on fault
tolerance. Our algorithms operate entirely on abstract topologies.  We
prove that the properties established by our analyses hold for every
concrete instantiation of the given abstract topology. \sysname
also guarantees that minimal changes to existing device configurations
are required when the network evolves to add or remove devices and
links. Our experiments with real-world topologies and policies show
that our abstractions and algorithms are effective, and that, for large
networks, \sysname synthesizes configurations two orders of magnitude
faster than systems that operate over concrete topologies.

%\ryan{Copied from conclusion for reference}
%We develop \sysname, the first system that can generate device configuration templates for large networks from high-level specifications of network topology and policy. \sysname is based on new abstractions for capturing parameterized network topologies, and their evolution, and algorithms to analyze the combined impact of topology and routing policy on the network's fault tolerance. Our analysis operates entirely in the abstract domain and guarantees correctness for all concrete instantiations of the topology. Experiments with many types of real-world topologies and policies show that our abstractions and analysis are precise and that, for large networks, configuration synthesis is two orders of magnitude faster than systems that operate over concrete topologies.

%We develop techniques for automated reasoning about end-to-end properties of
%abstract network topologies, and embody them in a network synthesis tool called
%\sysname. \sysname allows network operators to write a high-level routing policy
%over an abstraction of their network topology. From such a specification,
%\sysname synthesizes a collection of router configurations running the
%distributed Border Gateway Protocol (BGP) that are guaranteed to implement the
%centralized routing policy for any concrete instantiation of the abstract
%topology, and for any combination of network failures in the resulting concrete
%topology.
%
%Additionally, properties proven by \sysname over the abstract topology, such as
%reachability between a source and destination under k-failures, are also
%guaranteed to hold under any concrete instantiation of the abstract topology.
%
%Something something, expandable/incremental networks. Something something scales
%compilation to large networks. Something something, templates easier to
%understand.
%These strong guarantees allow operators to reason about the routing behavior of
%their network at a high-level abstraction, while also generating an efficient
%low-level implementation.
%
%In addition, operators are able to safely change or expand their network in any
%way, so long as the new resulting topology also respects the abstraction.
%
%We test \sysname out on ... blah blah blah

@@

%\vspace{0.1in} \noindent \textbf{CCS Concepts}\\ $\bullet$ Networks
%$\rightarrow$ {\em Network control algorithms; Network reliability; Network
%management;} $\bullet$ Software and its engineering $\rightarrow$ {\em
%Automated static analysis; Domain specific languages}

%\vspace{0.1in} \noindent \textbf{Keywords}\\ \Propane; Domain-specific Language;
%BGP; Synthesis; Compilation; Fault Tolerance; Distributed Systems

@@

Unfortunately, templates use the same low-level constructs as ordinary router configurations (\EG,
add a tag to this particular announcement; remove a tag from that announcement).  In both templatized
and non-templatized configurations, ensuring that a collection of low-level, local configurations
achieves some important global, network-wide policy, such as a guarantee of connectivity in the face of 
failures, is extremely challenging.
%
%Worse, operators can never be sure that their templates correctly implement the policy. %
%Formally verifying them is difficult; today's hand-generated templates have no particular semantics---which 
%policies they implement and for which topologies---other than those of the configurations obtained from 
%instantiating them.
%
In order to validate their templates, operators will typically first instantiate a template with appropriate
concrete parameters
and then test it using various scenarios.  In general, like in any complex software system, such testing is 
bound to be incomplete.
%Thus, operators validate templates by testing some concrete instantiations using
%simulation or verification tools~\cite{feamster+:rcc, batfish, era, arc, bagpipe}. 
Moreover, even if network operators were to instantiate their templates using their initial network 
configuration and to verify key properties using a tool such as Bagpipe~\cite{bagpipe}, the guarantees
provided would not hold as large networks evolve frequently over time.  In particular,
devices and links are sometimes taken offline for maintenance and sometimes added to expand
capacity.  Unfortunately, templates that
work for the current topology, may or may not work for future
topologies. Problems that occur may cause operators to make small, non-uniform, one-off changes to particular routers,
which defeats the purpose of a template system.  An even worse situation occurs when
operators feel obligated to update many (non-local) devices to extend or change their network.  
Such network-wide configuration changes entail a great deal of risk and may be highly
disruptive in production networks with live traffic.
%Ideally, network engineers would like some guarantees about the future, namely that 
%certain types of changes to the network topology may be (1) made \emph{locally}, and do not require
%updates of routers far from the source of the change, and (2) do not violate key properties, such
%as fault tolerance.
%Updating the templates, if found to not work for a future topology,
%may cause trickle-down, network-wide configuration changes that are highly
%disruptive in production networks with live traffic.
%Building sophisticated tools for validating templates is difficult

@@

To address the challenge of configuration synthesis in the presence of abstract roles, we present \sysname. 
%BGP, unlike link state protocols
%such as OSPF, is also particularly
%useful in our setting because it contains features that help us localize the effects of changes.
\sysname
allows operators to input \emph{abstract network topologies} in terms of roles
and their connectivity. For instance, they may specify roles for ``top-of-rack''
and ``aggregation" routers and specify that every top-of-rack router connects to
at least two aggregation routers (to tolerate the failure of a link to an
aggregation router). Other inputs to \sysname include the routing policy of the
network and its fault-tolerance requirements (\EG, the number of simultaneous link failures
to tolerate). For high-level specification of routing policy, we borrow notation from the original
\Propane system~\cite{propane}.  However, while \Propane policies refer to concrete devices,
\sysname policies refer to abstract roles.

Based on these inputs, \sysname generates one template per role. 
These templates specify routing policy using the Border Gateway Protocol (BGP).
BGP is a useful target for synthesis, as it is the standard protocol
for interdomain routing and it is also commonly used
within data centers due to its scalability properties.  However, it is far from the only control
plane protocol; synthesis of configurations for other common protocols such as OSPF is beyond the 
scope of this paper.

During synthesis, our compiler performs an important analysis over abstract topologies to determine
the fault tolerance properties of the specified policy.  This analysis determines the
number of failures require to disconnect one abstract location from another given the constraints
specified by the abstract topology.  The analysis is specified by a collection of inference rules
and we prove these inference rules are sound: any concrete instance of the abstract topology will
adhere to the given fault tolerance property. \dpw{Ryan: check this.}
%% first analysis determines whether a user policy can be implemented correctly using BGP in
%% the face of failures (\ie, given any number of failures, will the traffic flow along one of the 
%% specified paths if such a path is available).  The second analysis determines the number of failures
%% required to disconnect one abstract location from another.  
%% Our synthesis algorithm comes with a strong guarantee come with a strong
%% guarantee:  when the templates are instantiated with parameters, giving rise to concrete configurations,
%% and those concrete configurations  {\em
%% any} concrete topology that complies with the abstract topology, the resulting
%% network will correctly implement the routing policy and meet the fault-tolerance
%% requirements.

@@

\vspace{1em}
\noindent
\textbf{Contributions}: To summarize, our contributions are:
%
\begin{itemize}[noitemsep,nolistsep,label={\large\textbullet}]
\item New topology abstractions for network programming
based on graph homomorphisms and connectivity rules.
\item New algorithms for analyzing routing policy and fault tolerance over
abstract topologies.
%one which guarantees correct compilation and one which determines fault tolerance
%properties of network policy.
%Both algorithms provide guarantees for any
%concrete network satisfying the abstract connectivity invariants.
%\item Design of a template generation strategy that supports network
%evolution.
\item Implementation and evaluation of the \sysname compiler that generates
provably-correct BGP templates and is much faster
than compilers based on concrete topologies.
\end{itemize}

@@

  \end{minipage}
  \vspace{-.3em}
  \caption{\sysname core syntax.}
  \label{fig:syntax}
  %\vspace{-1.4em}
\end{figure}%

@@

  \hrule
  \vspace*{1em}
  \caption{Abstract k-disjoint path analysis inference rules.}
  \label{fig:inference-rules}
  \vspace{-.8em}
\end{figure*}

@@

The possibility of network failures exacerbates the difficulty of constructing correct configurations.
Link failures in networks occur frequently; it is not uncommon for a large network to experience dozens of failures in any given day~\cite{dc-failure-study}. However, existing tools~\cite{condor,propane} reason about fault-tolerance only for concrete topologies. \sysname provides substantially stronger guarantees: all possible concrete instantiations of an abstract topology satisfy the fault-tolerance policy.

@@

%
We frame satisfying the fault-tolerance policy provided by the user as an analysis problem over the structure of the PG. In particular, we develop an analysis that uses information embedded in the abstract topology to infer bounds on the number of edge-disjoint paths between pairs of concrete nodes.

@@

  %\vspace{1em}%
  \begin{minipage}[t]{.47\linewidth}
  \hdr{ABGP Syntax}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
     d    &   & & \textit{integer} \\
     c    &   & & \textit{community} \\
     l    &   & & \textit{location} \\
     t    &::=& \$x \BNFALT d.d.d.d/[d..d] & \textit{predicate} \\
     ns   &::=& \{ l_1, ~\dots,~ l_k \} & \textit{peers} \\
     ma   &::=& d : ({ns}_1, c_1) \rightarrow ({ns}_2, c_2) & \textit{match action} \\
     pc   &::=& ma_1, \dots, ma_k & \textit{prefix config} \\
     rc   &::=& t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k & \textit{router config} \\
     abgp &::=& l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k & \textit{abgp policy} \\%
  \end{array} \]%%

  \end{minipage}
  %
  %
  \begin{minipage}[t]{.49\linewidth}
  \hdr{Compilation to ABGP}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{l}
     \mathrm{compile}_\mathrm{ABGP}( [(t_1,PG_1,ord_1), \dots, (t_k,PG_k,ord_k)], G ) = \\
     ~~~~~ [~ l \rightarrow rc ~\vert~ l \in \mathrm{internal}(G.V), ~rc = \mathrm{append}_i~  \\
     ~~~~~~~~~~~~~~~ [~ t_i \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \mathrm{adjIn}(PG_i,m), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ bs=\{b ~\vert~ (b,q_n) \in pin \}, bs \neq \emptyset \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \mathrm{adjOut}(PG_i,m) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma = \mathrm{ord}_i(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] ~] \\
     \\
     \mathrm{compile}( p_1, \dots, p_k, G) = \\
     ~~~~~~ \mathrm{compile}_\mathrm{ABGP}([\mathrm{compile}_\mathrm{PG}(p_1,G), \dots, \mathrm{compile}_\mathrm{PG}(p_k,G)], G) \\
  \end{array} \]%
  \end{minipage}%

@@

%
For example, in the inequality $(S1,0,1) \leq (S1,1,0)$ holds since nodes on the left side of the PG can always match transitions made on the right hand side with respect to the $\geq_{rank}$ relation. This relation does not hold the other way around since $(S1,0,1) \ngeq_{rank} (S1,1,0)$. Therefore, advertisements received at $S1$ with tag $(1,0)$ must be preferred to those received at $S1$ with tag $(0,1)$.
%
Notice that in the abstract PG $(S,0,1) \leq (S,1,0)$ also holds.

@@

\para{mBGP}

@@

%By combining the tagging, filtering and preference mechanisms, we can generate safe BGP configurations. In general, configurations are generated by combining the per-prefix configurations in the same order specified in the policy.
Figure~\ref{fig:bgp-configs} (left) shows part of the final configuration for spine routers for the concrete and abstract policies in a vendor-neutral syntax.
%
For prefix $\True$ ($0.0.0.0/[0..32]$), the spine routers will match advertisements from peer N1 and N2. The match for N1 is preferred since it has a higher BGP local-preference attribute (110). If an advertisement from N1 is available the spine uses this and attaches the community tag $(1,0)$ before sending the route to all its peers ($*$). If an advertisement is only available from the backup N2, then it attaches the tag $(0,1)$ instead.
%
The template configuration matches any global prefix $\CD{\$GP}$ from any internal peer and re-advertises the route to all of its peers. For any local prefix it will allow an advertisement from any internal peer, and re-advertise the route to only other internal peers. The concrete configurations have a similar configuration for each local and global prefix.

%\vspace{2em}
%\begin{figure*}[t!]\small%

%  \hrulefill%
%  \vspace{1em}%

%  \begin{minipage}[t]{.46\linewidth}
%  \hdr{ABGP Syntax}{}
%  \vspace*{-1\baselineskip}
%  %
%  \[ \begin{array}{rclr}
%     d    &   & & \textit{integer} \\
%     c    &   & & \textit{community} \\
%     t    &::=& \$x \BNFALT d.d.d.d/[d..d] & \textit{predicate} \\
%     ns   &::=& \{ l_1, ~\dots,~ l_k \} & \textit{peers} \\
%     ma   &::=& d : ({ns}_1, c_1) \rightarrow ({ns}_2, c_2) & \textit{match action} \\
%     pc   &::=& ma_1, \dots, ma_k & \textit{prefix config} \\
%     rc   &::=& t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k & \textit{router config} \\
%     abgp &::=& l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k & \textit{abgp policy} \\%

%  \end{array} \]%%

%  \end{minipage}
%  %
%  %
%  \begin{minipage}[t]{.5\linewidth}
%  \hdr{Compilation}{}
%  \vspace*{-1\baselineskip}
%  %
%  \[ \begin{array}{l}
%     \text{compile}_\text{ABGP}( (t_1,PG_1,ord_1), \dots, (t_k,PG_k,ord_k), G ) = \\
%     ~~~~~ [~ l \rightarrow rc ~\vert~ \\
%     ~~~~~~~~~ l \in internal(G.V), \\
%     ~~~~~~~~~ rc = \mathit{append}_i~  \\
%     ~~~~~~~~~~~~~~~ [~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
%     ~~~~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_i, \\
%     ~~~~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG_i,m), \\
%     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) = \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{b ~\vert~ (b,q_n) \in pin \} \} \\
%     ~~~~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \} \\
%     ~~~~~~~~~~~~~~~~~~~~~ ma_j = ord_i(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] \\
%     \\
%     \text{compile}( p_1, \dots, p_k, G) = \\
%     ~~~~~~ \text{compile}_\text{ABGP}(\text{compile}_\text{PG}(p_1,G), \dots, \text{compile}_\text{PG}(p_k,G), G) \\
%  \end{array} \]%
%  \end{minipage}%

%  \vspace{1em}
%  \vspace{1em}%

%  \vspace*{-2\baselineskip}
%  \begin{minipage}[t]{1.01\linewidth}
%  \hdr{Policy Concretization}{}
%  \vspace*{-2\baselineskip}
%  %
%  \[ \begin{array}{lcl}
%     \\
%     \Con(\emptyset, \Gamma, f)      &=& \emptyset \\
%     \Con(l, \Gamma, f)              &=& \Sigma_i ~ f_i^{-1}(l) \\
%     \Con(r_1 \cup r_2, \Gamma, f)   &=& \Con(r_1,\Gamma,f) \cup \Con(r_2,\Gamma,f) \\
%     \Con(r_1 \cap r_2, \Gamma, f)   &=& \Con(r_1,\Gamma,f) \cap \Con(r_2,\Gamma,f) \\
%     \Con(!r, \Gamma, f)             &=& !\Con(r,\Gamma,f) \\
%     \Con(r^*, \Gamma, f)            &=& \Con(r,\Gamma,f)^* \\%

%     \Con(\Pfx ~\Path~ r_1, ~\dots~, r_k, \Gamma, f) &=&
%          \Pfx ~\Path~ \Con(r_1,\Gamma,f), ~\dots~, \Con(r_k,\Gamma,f)  \\%

%     \Con(\$x ~\Path~ r_1, ~\dots~, r_k, \Gamma, f) &=&%

%         [~ \Pfx ~\Path~ \Con(r_1,\Gamma,f) \cap \text{end}(l), ~\dots~, \\%

%         & & ~~~~~~~~~~~~~~~ \Con(r_k,\Gamma,f) \cap \text{end}(l) ~\vert~ (\Pfx,l) \in \Gamma(x) ~]  \\%

%     \Con(p_1, \dots, p_n, \Gamma,f) &=& \Con(p_1, \Gamma,f), \dots, \Con(p_n, \Gamma,f) \\%

%  \end{array} \]%
%  \end{minipage}%

%  \vspace{1em}
%  \vspace{1em}%

%  \begin{minipage}[t]{\linewidth}
%  \hdr{ABGP Concretization}{}
%  \vspace*{-2\baselineskip}
%  %
%  \[ \begin{array}{lcl}
%     \\
%     \Con(l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k,\Gamma,f,G)
%        & = &
%        \mathit{append}_i~ [~ \ell \rightarrow con(rc_i,\ell,\Gamma,f,G)  ~\vert~ \ell \in f^{-1}(l_i) ~]
%        \\
%     \Con(t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k,\ell,\Gamma,f,G)
%        & = &
%        \Con(t_1 \rightarrow {pc}_1,\ell,\Gamma,f,G), \dots, \Con(t_k \rightarrow {pc}_k,\ell,\Gamma,f,G)
%        \\
%     \Con(\Pfx \rightarrow {pc},\ell,\Gamma,f,G)
%        & = &
%        \Pfx \rightarrow \Con(pc,\text{true},\ell,\Gamma,f,G)
%        \\
%     \Con(\$x \rightarrow {pc},\ell,\Gamma,f,G)
%        & = &
%        [~ \Pfx \rightarrow \Con(pc, l=\ell, \ell,\Gamma,f,G) ~\vert~ (\Pfx, l) \in \Gamma(x) ~]
%        \\
%     \Con(ma_1, \dots, ma_k,o,\ell,\Gamma,f,G)
%        & = &
%        \Con(ma_1,o,\ell,\Gamma,f,G), \dots, \Con(ma_k,o,\ell,\Gamma,f,G)
%        \\%

%     \Con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),o,\ell,\Gamma,f,G)
%        & = & \textbf{if}~ ns_1 = \{\text{start}\} ~\text{and}~ o = \text{false} ~\textbf{then}~ \bullet \\
%        &   & \textbf{else}~ n_1 : ( \Con({ns}_1,\ell,\Gamma,f,G), n_2) \rightarrow (\Con({ns}_2,\ell,\Gamma,f,G),n_3)%

%        \\
%     \Con(\{ l_1, ~\dots,~ l_k \}, \ell, \Gamma,f,G)
%        & = &
%        \bigcup_i ~ \{ x ~\vert~ x \in f^{-1}(l_i),~ (x,\ell) \in G.E \}
%        \\
%  \end{array} \]%
%  \end{minipage}%

%  \vspace{1em}
%  \hrulefill%
%  \vspace{1em}%

%  \caption{ABGP syntax, compilation from product graphs, policy concretization, and ABGP concretization.}
%  \label{fig:concretization}
%\end{figure*}%

>>>>

\authorinfo{Ryan Beckett}{Princeton University}{rbeckett@cs.princeton.edu}
\authorinfo{Ratul Mahajan}{Microsoft Research}{ratul@microsoft.com}
\authorinfo{Todd Millstein}{University of California, Los Angeles}{todd@cs.ucla.edu}
\authorinfo{Jitendra Padhye}{Microsoft Research}{jpadhye@microsoft.com} 
\authorinfo{David Walker}{Princeton University}{dpw@cs.princeton.edu}

@@

\textbf{Abstract---}
We develop \sysname, a system to synthesize provably-correct
BGP configurations for large, evolving networks from high-level
specifications of topology, routing policy, and fault-tolerance
requirements. \sysname is based on new abstractions for capturing
parameterized network topologies and their evolution, and algorithms
to analyze the impact of topology and routing policy on fault
tolerance. Our algorithms operate entirely on abstract topologies.  We
prove that the properties established by our analyses hold for every
concrete instantiation of the given abstract topology. \sysname
also guarantees that minimal changes to existing device configurations
are required when the network evolves to add or remove devices and
links. Our experiments with real-world topologies and policies show
that our abstractions and algorithms are effective, and that, for large
networks, \sysname synthesizes configurations two orders of magnitude
faster than systems that operate on concrete topologies.

@@

@@

Unfortunately, templates use the same low-level constructs as ordinary router configurations (\EG,
add a tag to this particular announcement; remove a tag from that announcement).  In both templatized
and non-templatized configurations, ensuring that a collection of low-level, local configurations
achieves some important global, network-wide policy, such as a guarantee of connectivity in the face of 
failures, is extremely challenging.
%
%Worse, operators can never be sure that their templates correctly implement the policy. %
%Formally verifying them is difficult; today's hand-generated templates have no particular semantics---which 
%policies they implement and for which topologies---other than those of the configurations obtained from 
%instantiating them.
%
In order to validate their templates, operators will typically first instantiate a template with appropriate
concrete parameters
and then test it using various scenarios.  In general, like in any complex software system, such testing is 
bound to be incomplete.
%Thus, operators validate templates by testing some concrete instantiations using
%simulation or verification tools~\cite{feamster+:rcc, batfish, era, arc, bagpipe}. 
Moreover, even if network operators were to instantiate their templates using their initial network 
configuration and to verify key properties using a tool such as Bagpipe~\cite{bagpipe}, the guarantees
provided would not hold as large networks evolve frequently over time.  In particular,
devices and links are sometimes taken offline for maintenance and sometimes added to expand
capacity.  Unfortunately, templates that
work for the current topology, may or may not work for future
topologies. Problems that occur may cause operators to make small, non-uniform changes to particular routers,
which defeats the purpose of a template system.  An even worse situation occurs when
operators feel obligated to update many devices to extend or change their network.  
Such network-wide configuration changes entail a great deal of risk and may be highly
disruptive in production networks with live traffic.
%Ideally, network engineers would like some guarantees about the future, namely that 
%certain types of changes to the network topology may be (1) made \emph{locally}, and do not require
%updates of routers far from the source of the change, and (2) do not violate key properties, such
%as fault tolerance.
%Updating the templates, if found to not work for a future topology,
%may cause trickle-down, network-wide configuration changes that are highly
%disruptive in production networks with live traffic.
%Building sophisticated tools for validating templates is difficult

@@

To address the challenge of configuration synthesis in the presence of abstract roles, we present \sysname. 
%BGP, unlike link state protocols
%such as OSPF, is also particularly
%useful in our setting because it contains features that help us localize the effects of changes.
\sysname
allows operators to input \emph{abstract topologies} in terms of roles
and their connectivity. For instance, they may specify roles for ``top-of-rack''
and ``aggregation" routers and specify that every top-of-rack router connects to
at least two aggregation routers (to tolerate the failure of a link to an
aggregation router). Other inputs to \sysname include the routing policy of the
network and its fault-tolerance requirements (\EG, the number of simultaneous link failures
to tolerate). For high-level specification of routing policy, we borrow notation from the original
\Propane system~\cite{propane}.  However, while \Propane policies refer to concrete devices,
\sysname policies refer to abstract roles.

Based on these inputs, \sysname generates one template per role. 
These templates specify routing policy using the Border Gateway Protocol (BGP).
BGP is a useful target for synthesis, as it is the standard protocol
for interdomain routing and it is also commonly used
within data centers due to its scalability.  However, it is far from the only control
plane protocol; synthesis of configurations for other protocols such as OSPF is beyond the 
scope of this paper.

During synthesis, our compiler performs an important analysis over abstract topologies to determine
the fault tolerance properties of the specified policy.  This analysis determines a worst-case 
lower bound on the number of link failures require to disconnect one abstract location from another 
given the constraints specified by the abstract topology. Any concrete instance of the abstract topology will adhere to the given fault tolerance property.
%% first analysis determines whether a user policy can be implemented correctly using BGP in
%% the face of failures (\ie, given any number of failures, will the traffic flow along one of the 
%% specified paths if such a path is available).  The second analysis determines the number of failures
%% required to disconnect one abstract location from another.  
%% Our synthesis algorithm comes with a strong guarantee come with a strong
%% guarantee:  when the templates are instantiated with parameters, giving rise to concrete configurations,
%% and those concrete configurations  {\em
%% any} concrete topology that complies with the abstract topology, the resulting
%% network will correctly implement the routing policy and meet the fault-tolerance
%% requirements.

@@

\vspace{1em}
\noindent
\textbf{Contributions}: To summarize, our contributions are:
%
\begin{itemize}[noitemsep,nolistsep,label={\large\textbullet}]
\item New topology abstractions for network programming
based on graph homomorphisms and connectivity rules.
\item New algorithms for analyzing routing policy and fault tolerance over
abstract topologies.
%one which guarantees correct compilation and one which determines fault tolerance
%properties of network policy.
%Both algorithms provide guarantees for any
%concrete network satisfying the abstract connectivity invariants.
%\item Design of a template generation strategy that supports network
%evolution.
\item Implementation and evaluation of a \sysname compiler that generates
provably-correct BGP templates and is much faster
than compilers based on concrete topologies.
\end{itemize}

@@

  \end{minipage}
  \vspace{-.3em}
  \caption{\sysname core syntax.}
  \label{fig:syntax}
  %\vspace{-0.8em}
\end{figure}%

@@

  \hrule
  \vspace*{1em}
  \caption{Abstract k-disjoint path analysis inference rules.}
  \label{fig:inference-rules}
  \vspace{-1em}
\end{figure*}

@@

The possibility of network failures exacerbates the difficulty of constructing correct configurations.
Link failures in networks occur frequently; it is not uncommon for a large network to experience dozens of failures in any given day~\cite{dc-failure-study}. However, existing tools~\cite{condor,propane} reason about fault-tolerance only for concrete topologies. \sysname provides stronger guarantees: all possible concrete instantiations of an abstract topology satisfy the fault-tolerance policy.

@@

%
We frame satisfying the fault-tolerance requirements as an analysis problem over the structure of the PG. In particular, we develop an analysis that uses information embedded in the abstract topology to infer bounds on the number of edge-disjoint paths between pairs of concrete nodes.

@@

  %\vspace{1em}%
  \begin{minipage}[t]{.47\linewidth}
  \hdr{mBGP Syntax}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
     d    &   & & \textit{integer} \\
     c    &   & & \textit{community} \\
     l    &   & & \textit{location} \\
     t    &::=& \$x \BNFALT d.d.d.d/[d..d] & \textit{predicate} \\
     ns   &::=& \{ l_1, ~\dots,~ l_k \} & \textit{peers} \\
     ma   &::=& d : ({ns}_1, c_1) \rightarrow ({ns}_2, c_2) & \textit{match action} \\
     pc   &::=& ma_1, \dots, ma_k & \textit{prefix config} \\
     rc   &::=& t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k & \textit{router config} \\
     mbgp &::=& l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k & \textit{mbgp policy} \\%
  \end{array} \]%%

  \end{minipage}
  %
  %
  \begin{minipage}[t]{.49\linewidth}
  \hdr{Compilation to mBGP}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{l}
     \mathrm{compile}_\mathrm{mBGP}( [(t_1,PG_1,pref_1), \dots, (t_k,PG_k,pref_k)], G ) = \\
     ~~~~~ [~ l \rightarrow rc ~\vert~ l \in \mathrm{internal}(G.V), ~rc = \mathrm{append}_i~  \\
     ~~~~~~~~~~~~~~~ [~ t_i \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \mathrm{adjIn}(PG_i,m), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ bs=\{b ~\vert~ (b,q_n) \in pin \}, bs \neq \emptyset \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \mathrm{adjOut}(PG_i,m) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma = \mathrm{pref}_i(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] ~] \\
     \\
     \mathrm{compile}( p_1, \dots, p_k, G) = \\
     ~~~~~~ \mathrm{compile}_\mathrm{mBGP}([\mathrm{compile}_\mathrm{PG}(p_1,G), \dots, \mathrm{compile}_\mathrm{PG}(p_k,G)], G) \\
  \end{array} \]%
  \end{minipage}%

@@

%
For example, in the inequality $(S1,0,1) \leq (S1,1,0)$ holds since nodes on the left side of the PG can always match transitions made on the right hand side with respect to the $\geq_{rank}$ relation. This relation does not hold the other way around since $(S1,0,1) \ngeq_{rank} (S1,1,0)$. Therefore, advertisements received at $S1$ with tag $(1,0)$ must be preferred to those received at $S1$ with tag $(0,1)$.
%
Notice that in the abstract PG $(S,0,1) \leq (S,1,0)$ also holds. This leads to the following observation:

@@

\para{mBGP}
To characterize compilation we first introduce a simple, vendor independent configuration language for the BGP protocol called \mbgp. The syntax for \mbgp is shown in Figure~\ref{fig:concretization} (left). An \mbgp policy consists of a sequence of router configurations (one for each internal topology location $l$). A router configuration is an ordered sequence of a predicate describing the traffic, and a predicate configuration. A predicate is either a template variable $\$\mathrm{x}$ or a prefix. A predicate configuration is a collection of match action statements, where each match action indicates that the router will match advertisements from any of a set of peers $ns_1$ with a particular community tag $c_1$ with local preference $d$, before exporting the route to another set of peers $ns_2$ with a new community tag $c_2$.

@@

Figure~\ref{fig:concretization} (right) defines compilation from \sysname to \mbgp. It proceeds by compiling constraints $p_i$ in the original \sysname policy to a tuple of: the predicate $t_i$, the product graph $PG_i$, and the preference function $pref_i$. These tuples are passed the the $\mathrm{compile}_\mathrm{mBGP}$ function, along with the network topology $G$. For each internal router in the topology $l$, and each predicate $t_i$ in the \sysname policy, compilation goes through each node $m$ for $l$ in $PG_i$, and groups the inbound neighbors of $m$ by tag ($q_n$) into sets ($in$). It allows imports from these neighbors before exporting to the outbound neighbors of $m$. The local preference for these imports is given by $\mathrm{pref}_i(m)$.

Figure~\ref{fig:bgp-configs} (left) shows part of the generated \mbgp configuration for spine routers for both the concrete and abstract policies. For brevity, we using the symbol ($*$) to denote the set of all neighbors and omit tags when irrelevant.
%
For prefix $\True$ ($0.0.0.0/[0..32]$), the spine routers will match advertisements from peer N1 and N2. The match for N1 is preferred since it has a higher BGP local-preference attribute (110). If an advertisement from N1 is available the spine uses this and attaches the community tag $(1,0)$ before sending the route to all its peers ($*$). If an advertisement is only available from the backup N2, then it attaches the tag $(0,1)$ instead.
%
The template configuration matches any global prefix $\CD{\$GP}$ from any internal peer and re-advertises the route to all of its peers. For any local prefix it will allow an advertisement from any internal peer, and re-advertise the route to only other internal peers. The concrete configurations for S1 and S2 obtained from compilation for the concerete PG from Figure~\ref{fig:example-compilation} have a similar structure for each local and global prefix where local routes are reflected downward, while global routes are advertised to all peers.

\para{Concretization}
The similar structure between the spine template and concrete configurations is not a coincidence.  We formalize this observation by defining a two concretization function ($con$), one for \sysname policies and another for \mbgp policies. 
%
Concretization takes a context $\Gamma : \mathit{Var} \rightarrow 2^{\mathit{Prefix} \times V}$ that maps each template variable to a set of pairs of a concrete prefix and topology location where the prefix is owned.

Both concretization functions traverse the policy and substitute each instance of a topology loction $l$ in the template policy with the set of all concrete locations that map to $l$, given by the inverse homomorphism $f^{-1}(l) = \{l' ~\vert~ f(l') = l \}$. Additionally, whenver a pair $(pfx,l) \in \Gamma(x)$, then a new entry is added to the concretized policy where $pfx$ replaces $\$\mathrm{x}$ and adds the constraint that traffic ends at $l$ ($\CD{\End(l)}$).
%
For example, the spine template in Figure~\ref{fig:bgp-configs}, is obtained by substituting $\{ A1,A2 \}$ for $AG$ and $\{ A3,A4 \}$ for $AL$ and by also replacing the entry for {\small \$GP} with entries for {\small GP1} and {\small GP2} given by the context (\EG, a database).

Our main theoretical result is that the compilation and concretization functions commute:
